Differentially Private Bayesian Inference

### 2018-04-03 main.tex
dilation property for expomech

		This need to be discuss further.

@@

		This need to be discuss further.

@@

So, we only need to proof it in two cases where $\lambda > 0, u(x,r) < 0$ and $\lambda < 0, u(x,r) > 0$.

>>>>

		% This need to be discuss further.
		We can have:
		\begin{equation*}
		\lambda\leq \ln (1 - \frac{S(x)}{\hat{s}}) 
		\end{equation*}

@@

		% This need to be discuss further.
		We can have:
		\begin{equation*}
		\lambda\geq \ln (1 - \frac{S(x)}{\hat{s}}) 
		\end{equation*}
		Since $\lambda > 0$ is the pre-condition, it can be inferred that the property cannot hold under this case.

@@

In conclusion, the dilation property holds under these conditions that: $\lambda u(x,r) > 0$ or $\lambda > 0, u(x,r) < 0, \lambda \leq \ln (1 - \frac{S(x)}{\hat{s}})$.

% So, we only need to proof it in two cases where $\lambda > 0, u(x,r) < 0$ and $\lambda < 0, u(x,r) > 0$.

% We take the absolute value of utility function, then there is only one case we need to discuss: $(1 - e^{\lambda}) |\hat{s}| \leq S(x)$, $\lambda < 0$.
